---
title: "Clustering Anchor Hits"
output:
  html_document:
    df_print: paged
---

# Setup
Load our libraries first
```{r}
list.of.packages <- c("tidyverse", "here", "reshape2", "ggraph", "tidygraph")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
library(here)
library(tidyverse)
library(reshape2)
library(ggraph)
library(tidygraph)
```

# Load data and set parameters
The gene hits data must have a 'Gene ID' column with NCBI gene ID's. All other columns are treated as metainformation.
```{r}
gene_hits <- read_csv(here('data','PARP1_gene_hits.csv'))
head(gene_hits)
```
 Gene effect scores can be downloaded from the [depmap](https://depmap.org/portal/download/).
```{r}
depmap_cutoff <- 0.2 # Correlation cutoff
depmap_data <- read_csv(here('data', 'Achilles_gene_effect.csv')) %>%
    rename(cell = X1)
depmap_data[1:10,1:10]
```

# Create Network
Now we want to extract the relevant columns and create our network.

```{r}
depmap_ids <- str_extract(colnames(depmap_data), '(?<=\\()[0-9]*')
relevant_columns <- depmap_ids %in% gene_hits$`Gene ID`
relevant_depmap <- depmap_data[,relevant_columns]
correlation_mat <- cor(relevant_depmap, use ='pairwise.complete.obs') # use pairwise complete to allow for NA's for XX cells
# Remove duplicate and self edges
correlation_mat[abs(correlation_mat) < depmap_cutoff] <- NA 
diag(correlation_mat) <- NA
melted_cors <- melt(correlation_mat, na.rm = TRUE, value.name = 'correlation')
head(melted_cors)
```

```{r}
depmap_net <- as_tbl_graph(melted_cors, directed = FALSE) %>% # Turn the edge table into a tbl graph for easy manipulation 
  activate(nodes) %>%
  mutate(`Depmap Gene Name` = word(name), 
         `Gene ID` = as.numeric(str_extract(name, '(?<=\\()[0-9]*'))) %>%
  inner_join(gene_hits)
depmap_net
```

# Clustering and Visualization
The [tidygraph](https://github.com/thomasp85/tidygraph) package has a wide array of functionality for analyzing networks. Here we will cluster our network and visualize one of the clusters using ggraph. 

```{r}
node_weight = 'all' # Which column of metadata to size nodes by 
clustered_depmap_net <- depmap_net %>%
  activate(nodes) %>%
  mutate(group = group_louvain(weights = abs(correlation)))
cluster <- clustered_depmap_net %>%
  filter(group == 2)
ggraph(cluster, layout = 'kk') +
  geom_edge_link(aes(color = as.factor(sign(correlation)), 
                     width = abs(correlation))) +
  scale_edge_width(range = c(0.3,2)) +
  scale_edge_color_manual(values = c(`-1` = 'pink', `1` = 'skyblue')) +
  theme_void() +
  labs(edge_width = 'Correlation', edge_color = 'Edge Sign') +
  geom_node_point(aes(size = abs(all),
                      color = as.factor(sign(all))), 
                  fill = 'white', pch = 21) +
  scale_color_manual(values = c(`-1` = '#ef8a62', `1` = '#67a9cf')) +
  scale_size(range = c(1, 4)) + 
  labs(color = 'Node Sign', size = 'Score') +
  geom_node_text(aes(label = name), size = 3, 
                                    repel = TRUE, point.padding = 0, 
                                    min.segment.length = 0.1)
```



